### 2014-09-11 A1/writeup/writeup.tex
worked on the writeup a bit

\section*{Data and Methods}
For our analysis, we use a dataset consisting of 500k Amazon ``fine foods'' reviews taken from 2002 to 2012 \cite{mcauley2013amateurs}.

\section*{Results}

\section*{Conclusions}

Notably, Mudambi et al. find that what makes a review helpful depends strongly on whether the product in question can be classified as a experience good, which cannot be truly evaluated until a consumer has \emph{experienced} it, or search good, which a customer can make most evaluations about prior to purchase \cite{mudambi2010makes}. Because our dataset consisted of the fine foods section of Amazon, most of the products in our dataset constitute experience goods. Consequently, our preliminary results might not extend to datasets that have a higher proportions of search goods.

>>>>

\section*{Data and Methods}
For our analysis, we use a dataset consisting of 500k Amazon ``fine foods'' reviews taken from 2002 to 2012 \cite{mcauley2013amateurs}. The information of interest contained in a given review includes the product ID to which it corresponds, the number of helpful/unhelpful votes it has recieved, and the text of that review. We restrict our consideration to 300 reviews in our dataset with the most total helpful votes, summed over all reviews of that product.

For each review, we remove all punctuation, captialization, and run each resulting token through a Porter stemmer. Next, we create a vector space representation of a review using unigram tfidf features, where idf is computed with respect to a given product, rather than the whole dataset. This interpretation treats a given products' reviews as a corpus. Stemmed tokens that appear less than (PUT SOMETHING HERE) times or in more than (PUT SOMETHING HERE) percent of the reviews for a given product are discarded.

Next, the high-dimensional sparse per-document vectors are projected to an optimal linear subspace of (PUT PCA DIM HERE) dimensions using PCA. After the dimensionality reduction step, reviews are clustered using a modified k-means clustering algorithm. Because many clustering methods, including k-means, are highly sensitive to outliers (for instance, the k-means objective utilizes an $L_2$ norm, so points far from cluster centers are very influential) and our goal is to use clustering for outlier detection, we implemented a slightly modified version of k-means, \emph{constrained k-means}, that enforces a minimal number of points in each cluster.

(MAYBE INPUT PICTURES ABOUT WHY CONSTRAINED K-MEANS IS REQUIRED?)

Given $k$, the number of desired clusters, and $0 < p < \frac{n}{100k}$, the minimum proportion of the data that must be in each cluster, constrained k-means returns a reasonable clustering of the data that satisfies these parameters. To ensure that clusters are ``big enough,'' the method begins by running normal k-means, and checking cluster size. If the data is spread properly with respect to $p$, that clustering is returned. Otherwise, (k+1)-means is executed, and the two clusters with the closest centers are merged to produce k-means. If the (k+1)-means + 1 merge fails as well, (k+2)-means + 2 merges is executed, and so on. In this way, constrained k means consists of two steps: a flat clustering step, and a hirearchical clustering step.

After executing constrained k-means, we assign a ``uniqueness'' score to each clustered review by finding the distance between its vector representation and the closest cluster center. Ideally, the clustering process allows for up to (NUM CLUSTERS) ``prototypial'' review types to not be considered unique. If a review is far from each of the cluster centers, it is assigned a high uniqueness score.

Finally, for a given product, we run a logistic regression of uniquness on a new binary value ``helpfulness.'' We say a review is helpful if it has at least one helpful vote and more than $60\%$ of its helpful votes are positive. We are interested, in particular, in the resulting logistic regression coefficient on helpfulness. If this coefficient is generally positive over all products in our dataset, we conclude that uniqueness positively influences helpfulness. Conversely, if this coefficient is generally negative, uniqueness is a negative predictor of helpfulness.
\section*{Results}

\section*{Conclusions}
(DISCUSSION ABOUT RESULTS)

Notably, Mudambi et al. find that what makes a review helpful depends strongly on whether the product in question can be classified as a experience good, which cannot be truly evaluated until a consumer has \emph{experienced} it, or search good, which a customer can make most evaluations about prior to purchase \cite{mudambi2010makes}. Because our dataset consisted of the fine foods section of Amazon, most of the products in our dataset constitute experience goods. Consequently, our preliminary results might not extend to datasets that have higher proportions of search goods.

Finally, we recognize that our metric of uniqueness could be improved upon. For instance, it would be interesting to include bigram features in our vector space review representation. Also, our consideration is limited to extremely simple lexical review features only. A more complete analysis, for instance, might include a subset of the dozens of more complex potential review features used by Ghose and Ipeirotis \cite{ghose2011estimating}. Our analysis also doesn't control for reviewer characteristics, which, given the complex social structure potentially underlying review sites like Amazon, is a potential avenue for future exploration.
